$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
added ref to two-loop Higgs papers from SARAH.

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and for the light Higgs we
use the leading two-loop contributions from \cite{King:2005jy} which
are a generalsiation of the correctsions in the MSSM and NMSSM
calculated using effective field theory techniques
\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
parameter space, the equivalent MSSM fine tuning expressions were
implemented into a modified version of SOFTSUSY 3.3.10
\cite{Allanach:2001kg}.  For consistency with the results produced in
the $E_6$ models, and for computational speed, for our main scans only
the dominant one- and two-loop corrections to the CP-even Higgs masses
were included.  Finally, in all of the results below the fine tuning
was evaluated at the scale $Q = M_{\textrm{SUSY}} =
\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
M_{\textrm{SUSY}}$.

>>>>

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and for the light Higgs we
use the leading two-loop\footnote{Two-loop corrections calculated for
  a non-minimal SUSY model may now also be obtained from SARAH
  \cite{Goodsell:2014pla,Goodsell:2015ira}.} contributions from
\cite{King:2005jy} which are a generalsiation of the correctsions in
the MSSM and NMSSM calculated using effective field theory techniques
\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
parameter space, the equivalent MSSM fine tuning expressions were
implemented into a modified version of SOFTSUSY 3.3.10
\cite{Allanach:2001kg}.  For consistency with the results produced in
the $E_6$ models, and for computational speed, for our main scans only
the dominant one- and two-loop corrections to the CP-even Higgs masses
were included.  Finally, in all of the results below the fine tuning
was evaluated at the scale $Q = M_{\textrm{SUSY}} =
\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
M_{\textrm{SUSY}}$.
